\begin{thebibliography}{99}

\bibitem{hu2022lora}
E.J. Hu, Y. Shen, P. Wallis, Z. Allen-Zhu, Y. Li, S. Wang, L. Wang, W. Chen (2022),
``LoRA: Low-Rank Adaptation of Large Language Models'',
\textit{International Conference on Learning Representations (ICLR 2022)}.

\bibitem{dettmers2023qlora}
T. Dettmers, A. Pagnoni, A. Holtzman, L. Zettlemoyer (2023),
``QLoRA: Efficient Finetuning of Quantized LLMs'',
\textit{Advances in Neural Information Processing Systems (NeurIPS 2023)},
Vol. 36, pp. 10088--10115.

\bibitem{yang2025qwen3}
A. Yang et al. (2025),
``Qwen3 Technical Report'',
\textit{arXiv preprint arXiv:2505.09388}.

\bibitem{guha2023legalbench}
N. Guha, J. Nyarko, D.E. Ho, C. R\'{e} et al. (2023),
``LegalBench: A Collaboratively Built Benchmark for Measuring Legal Reasoning
in Large Language Models'',
\textit{Advances in Neural Information Processing Systems (NeurIPS 2023)},
Vol. 36, pp. 44123--44279.

\bibitem{colombo2024saullm}
P. Colombo, T.P. Pires, M. Boudiaf et al. (2024),
``SaulLM-7B: A Pioneering Large Language Model for Law'',
\textit{arXiv preprint arXiv:2403.03883}.

\bibitem{nguyen2025vlqa}
T.-M. Nguyen, H.-T. Nguyen, T.-K. Dao, X.-H. Phan, H.-T. Nguyen,
T.-H.-Y. Vuong (2025),
``VLQA: The First Comprehensive, Large, and High-Quality Vietnamese
Dataset for Legal Question Answering'',
\textit{arXiv preprint arXiv:2507.19995}.

\bibitem{ha2024vibidlqa}
N.T. Ha, T.-P. Nguyen, K.T. Trung et al. (2024),
``Vietnamese Legal Question Answering: An Experimental Study'',
\textit{Proc. 16th International Conference on Knowledge and
System Engineering (KSE 2024)}, IEEE, pp. 440--446.

\bibitem{son2024vietnamese}
P.T. Son, N.D. Hieu, N.D. An, D.V. Sang (2024),
``Improving Vietnamese Legal Document Retrieval Using Synthetic Data'',
\textit{arXiv preprint arXiv:2412.xxxxx}.

\bibitem{ghosh2023dale}
S. Ghosh, C.K. Evuru, S. Kumar et al. (2023),
``DALE: Generative Data Augmentation for Low-Resource Legal NLP'',
\textit{arXiv preprint arXiv:2310.15799}.

\bibitem{wang2022self}
Y. Wang, Y. Kordi, S. Mishra, A. Liu, N.A. Smith,
D. Khashabi, H. Hajishirzi (2022),
``Self-Instruct: Aligning Language Models with Self-Generated Instructions'',
\textit{arXiv preprint arXiv:2212.10560}.

\bibitem{luan2025minlegal}
N.D. Luan, K.N. Van (2025),
``MinLegal at VLSP2025-LegalSLM: A Two-Stage LoRA-to-Full Fine-tuning
Approach for Vietnamese Legal Small Language Models'',
\textit{Proceedings of VLSP 2025}. (Hạng 2, score 0.7947)

\bibitem{quang2025bosch}
T.M. Quang, N.X. Phi, N.V. Tai, P.M. Toan, D.V. Thin (2025),
``Bosch@AI\_Team at LegalSML 2025: Vietnamese Legal Small Language
with Domain Adaptation and Aspect-based Data Synthesis'',
\textit{Proceedings of VLSP 2025}. (Hạng 1, score 0.8108)

\bibitem{unsloth2024}
Unsloth AI (2024),
``Unsloth: Faster and Memory-Efficient LLM Fine-tuning'',
\textit{Phần mềm mã nguồn mở}. \url{https://github.com/unslothai/unsloth}.

\bibitem{anthropic2025claude}
Anthropic (2025),
``Claude Haiku 4.5'',
\textit{Tài liệu kỹ thuật}. \url{https://www.anthropic.com}.

\bibitem{hf_peft}
Hugging Face (2024),
``PEFT: Parameter-Efficient Fine-Tuning'',
\textit{Hugging Face Documentation}.
\url{https://huggingface.co/docs/peft}.

\bibitem{hf_lora_conceptual}
Hugging Face (2024),
``LoRA Conceptual Guide'',
\textit{Hugging Face Documentation}.
\url{https://huggingface.co/docs/peft/conceptual_guides/lora}.

\bibitem{hf_qlora}
Hugging Face (2024),
``QLoRA: Efficient Finetuning of Quantized LLMs'',
\textit{Hugging Face Blog}.
\url{https://huggingface.co/blog/4bit-transformers-bitsandbytes}.

\bibitem{hf_quantization}
Hugging Face (2024),
``Quantization'',
\textit{Hugging Face Documentation}.
\url{https://huggingface.co/docs/transformers/quantization}.

\bibitem{lightning_lora}
Lightning AI (2024),
``Understanding LoRA'',
\textit{Lightning AI Blog}.
\url{https://lightning.ai/pages/community/lora-insights}.

\bibitem{towardsdatascience_lora}
S. Raschka (2023),
``Understanding LoRA -- Low-Rank Adaptation For Finetuning Large Models'',
\textit{Towards Data Science / Medium}.
\url{https://magazine.sebastianraschka.com/p/lora-and-dora-from-scratch}.

\end{thebibliography}
